Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-20 paper.tex
update

We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.

@@

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.

@@

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$. The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$. The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.

@@

$E = \{e_{1}, e_{2},... e_{n} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.

$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$

\textbf{QoS Model in Weighted DAG}

\subsection{Quality of Service}\label{Quality of Service and Composition Constructs}
According to \cite{zeng2003quality}, four most often considered QoS parameters are response time, cost, reliability and availability described as follows:
\begin{itemize}
\item \textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.
\item \textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service
\item \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame.
\item \textit{Availability} ($A$) is the probability that a web service is accessible.
\end{itemize}
The aggregation value of QoS attributes for a composite service varies with respect to different constructs, which reflects how services associated with each other in a service composition \cite{zeng2003quality}. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:
\subsubsection{Sequence construct}
all involved atomic services associated with a sequence construct are executed in a definite sequence order. The aggregation value for total time ($T$) and total cost ($C$) is as the sum of time and cost of web services involved respectively. The overall availability and reliability in a sequence construct are calculated by multiplying their corresponding availability and reliability of each web service in probability theory. This construct is shown in Fig. \ref{sequence}.
\subsubsection{Parallel construct}
Web services in a parallel construct are executed concurrently. The QoS aggregation value for total cost, availability and reliability are the same as these in sequence construct while the Total time ($T$) is determined by the most time-consuming path in the composition flow of the solution. This construct is presented in Fig. \ref{parallel}.

\begin{figure}[h]
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=2in]{sequence.pdf}\hfill\space\\[0.2cm]
$T=\sum\limits^m_{n=1}t_n$ \hfill $C=\sum\limits^m_{n=1}c_n$ \hfill
$A=\prod\limits^m_{n=1}a_n$ \hfill $R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Sequence construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{sequence}
%\end{figure}
\vspace{0.2cm}
%\begin{figure}
\centerline{
\fbox{
\begin{tabular}{p{0.6\linewidth}}
\space\hfill\includegraphics[width=1.4in]{parallel.pdf}\hfill\space\\[0.2cm]
\space\hfill$T=MAX\{t_n|n\in\{1,\ldots,m\}\}$\hfill\space\\[0.2cm]
$C=\sum\limits^m_{n=1}c_n$ \hfill $A=\prod\limits^m_{n=1}a_n$ \hfill
$R=\prod\limits^m_{n=1}r_n$
\end{tabular}}}
\caption{Parallel construct and calculation of its QoS properties
\cite{yu2013adaptive}.}
\label{parallel}
\end{figure}

>>>>

We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of three main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model.
\vspace{0.3cm}

@@

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a set of $S$, where all the $S$ are registered.
\vspace{0.3cm}

@@

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$. The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$. The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.
\vspace{0.3cm}

@@

$E = \{e_{1}, e_{2},... e_{m} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.

$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$
\vspace{0.5cm}

\textbf{QoS Model in a Weighted DAG}
Four most often considered QoS parameters \cite{zeng2003quality} are response time, cost, reliability and availability described as follows:\textit{Response time} ($T$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received.\textit{Cost} ($C$) is the amount of money that a service requester has to pay for executing the web service. \textit{Reliability} ($R$) is the probability that a request is correctly responded within the maximum expected time frame. \textit{Availability} ($A$) is the probability that a web service is accessible.

	The aggregation value of QoS in a DAG with respect to different constructs, which reflects how services associated with each other in a service composition. Here we consider two composition constructs: sequence and parallel constructs, in building the composition web service. The QoS calculation models are described as follows:

\textbf{Definition 5.} $V_{A}(WG)$ is a function that given a $WG$, a aggregated $availability$ value is returned, which is defined as :
$V_{A}(WG)=\prod\limits^n_{k=1}a_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 6.} $V_{R}(WG)$ is a function that given a $WG$, a aggregated $reliability$ value is returned, which is defined as :
$V_{R}(WG)=\prod\limits^n_{k=1}r_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 7.} $V_{C}(WG)$ is a function that given a $WG$, a aggregated cost value is returned, which is defined as :
$V_{C}(WG)=\sum\limits^n_{k=1}c_k$, for all ${S_1, S_2, ... S_n} \subset V$.

\textbf{Definition 8.} $V_{T}(WG)$ is a function that given a $WG$, a aggregated time value is returned, where  $T$ is determined by the most time-consuming path in the composition flow of the solution, which is defined as :
$V_{T}(WG)$ $=MAX\{timePath(WG)_n$ $|n\in\{1,\ldots,m\}\}$, where m is the number of $timePath$.

\vspace{0.5cm}

\textbf{Composition Problem}
A set of semantic web services $S$ are chained as a weighted DAG composition mode $WG$ when a composition task $Comp.T$ is requested by users. The composition problem considered in this paper satisfying the follows:
